---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# standardization

<!-- badges: start -->
<!-- badges: end -->

The goal of standardization is to standardize numbers in a given numeric vector.

## Installation

You can install the released version of standardization from [CRAN](https://CRAN.R-project.org) with:

``` r
devtools::install_github("ahushirley/standardization")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(standardization)
m <- c(2, 3, 5, 19, 30)
std_score(m)
```

## Process of making this R package:
1. Load `devtools` using the code `library(devtools)`.
2. Call `create_package()` to initialize a new package in a directory on computer.
3. Make the R package to a Git repository using `use_git()`.
4. Call `use_r("function_name")` to create and opens a script below R/.
5. After writing the function `std_score()`, call `load_all()` to make this function available for interactive use.
6. Use `check()` to check the R package.
7. Manually edit the title, name and description in *DESCRIPTION* file, and call `use_mit_license()` to get a license.
8. Call `library(roxygen2)`, go to *Code -> Insert Roxygen Skeleton* and manually edit the documentation (title, arguments, outputs, examples and etc).
9. Run `document()` to update documentation and load the R package.
10. Create tests by calling `use_testthat()` and `use_test("test_name")`, and then manually write tests in the created R file.
11. Add dependencies by calling `use_package("package_name")`.
12. Run `use_readme_rmd()` to generate README.rmd file and manually edit it.
13. Call `build_readme()` to knit to an .md file and check errors in .rmd file
14. Call `use_vignettes("function_name")` and manually edit the vignettes in the created .rmd file.
15. Call `build_vignettes()` to update vignettes for the package.
16. Finally `check()` and `Install and Restart` R session to test function.





